### 2023-04-14 paper/paper.tex
Paper

\documentclass{article}
\usepackage{amsmath}
\usepackage{ragged2e}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{pmboxdraw}
\usepackage{graphicx} \graphicspath{
{./images/} }
\usepackage{indentfirst}
\usepackage{multicol}
\usepackage[a4paper, total={6.5in, 8.5in}]{geometry}
\DeclareSymbolFont{letters}{OML}{ztmcm}{m}{it}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{wrnote}{Writing note}
\newtheorem{proof}{Proof}

@@

The emergence of new computational models has provided neuroscientific research
with novel methods for extracting significant insights from experimental results.
This paper takes a computational approach to challenges arising in the analysis
of transcranial stimulation (TMS) data. We argue that conducting TMS experiments
under the double-pulse paradigm enables the use of machine learning models. In
particular, we formulate pulse-specific measures of relative amplitude between
paired and test pulses. These has potential implications in both $a.$ the
production of evidence and $b$. the diagnosis of clinical disorders.

@@

In the context of this paper, we shall term any coefficient
that serves to represent the proportional relationship
between the potentials evoked by paired and test pulses a
\textit{measure of relative amplitude}.

The goal of this paper is to provide pulse-specific measures of relative
amplitude. This is, coefficients that represent the relative amplitude of each
individual paired pulse with respect to the set of test pulses in an
experimental session. The purpose of this endeavor is to keep data resolution
at its highest, which on its turn allows for the implementation of data-driven
artificial intelligence in the analysis of the 
experimental results. Thus, from a computer science perspective, our objective is
constrained to the sphere of feature engineering.

@@

\section{Data collection}

We used data collected across $N = ?$ subjects at the \textit{Laboratory for the
Study of Slow-wave sleep activity}, University of Pennsylvania, with $H = ?$
healthy controls and $D = ?$ diagnosed with major depressive disorder (MDD).
Transcranial magnetic stimulation of the motor cortex was elicited to them after
a night of baseline sleep and after a night of slow-wave disruption (SWD) sleep.
Motor evoked potentials were measured via an electrode (?) placed on the
subjects' thumb (?). In the slow-wave disruption session, an auditory stimulus with
sufficient strength to interrupt the normal occurrence of slow-wave sleep, yet
not strong enough to wake the subjects, was elicited. This experimental setting
produces four distinct categories, two depending on the subject group and two on
the type of sleep session underwent, as shown in the table below.

@@

\begin{tabular}{ |p{2cm}|p{2cm}|p{2cm}|  }
\hline
& Baseline & Slow-wave disruption \\
\hline
Healthy control & HC BL & HC SWD \\
\hline
Major depressive disorder & MDD BL & MDD SWD \\
\hli
\end{tabular}

@@

Each observation in the data was a specific experimental sample resulting
from an individual transcranial stimulation. The original features of the data
were:

\begin{enumerate}
    \item An $EMG$ variable with the EMG peak-to-peak of each observation.
    \item A $Label$ categorical feature, which encoded the group of
        the subject of each observation, was the target variable. 
    \item An $ISI$ feature that econded the inter-stimulus interval of each
        pulse. A value of $-1$ indicated that the given pulse was a test pulse (no
        inter-stimulus interval).
\end{enumerate}

\section{Limitations of the traditional analysis}

Measures of relative amplitude in neuroscience are generally computed at the
subject level by repeatedly taking averages in the following manner. First, the
quotient of the average paired-pulse and the average test pulse is found per
every subject. Secondly, those quotients are averaged out across all subjects in
a subject group. This is reasonable, since hypotheses generally deal with
differences across subject groups.

Two major limitations arise from this method. The principle one is the fact that
it implies greatly downscaling the data resolution Secondly, potentials evoked
by test and paired pulses present a very high variance (Rossini et. al., 20015;
Orth, Snijders and Rothwell, 2003; Wassermann, 2002), which —being that it is a
quotient of two means—  raises questions about the quality of the representation
where relatively few pulses are elicited.

When considering the size of the data across multiple experimental subjects,
this shrinkage in data resolution is far from being negligible. And in times
when scientific inquiry can greatly benefit from forms of artificial
intelligence that rely on large amounts of data (e.g. machine learning), it is
clearly limiting to only count with low-resolution measures to interpret
experimental results.

Considering the limitations of the traditional approach, this paper proposes two
pulse-specific relative amplitude measures. This allows for otherwise unfeasible
computational analyses of TMS data, such as the use of machine learning (ML) models
for the detection of different pulse-response patterns among different groups of
clinical subjects.

To empirically test the validity of these measures, we evaluated whether they
improved the performance of a classification model, and in what degree. (We
chose a classification model for practical reasons --namely, because the
samples in our data were conveniently labeled by subject group and sleep
session).

In order to do this, we defined a random forest model in Python under the
following parameters: \ldots

The model was tasked with classifying every observation with the appropriate subject
label. In other words, it was set out to infer, based on the properties of each
transcranial stimulation response, the group of the subject upon which the
stimulation was elicited, as well as the type of sleep session after which it
occurred.

The model was first trained on the raw data, with the features described in
\textbf{3.1}. Then, it was trained with the inclusion of one or many engineered
features of relative amplitude (see section \textbf{4}). These features were
computed for each observation using the Julia programming language.

As stated earlier, action potentials evoked by transcranial magnetic
stimulations follow a Gamma distribution that is very close to the exponential.
(see \textbf{Statistics} section). Experimentation has shown that the inclusion
of weighted variants of the features defined above greatly improves the
performance of a random forests model (see \textbf{Empirical results}).

Thus, our hypothesis is that pulse-specific measures of relative
amplitude will significantly improve a random forest's performance.

The following section (\textbf{Cite section}) defines the proposed measures of
relative amplitude. In section \textbf{Results}, we show the impact of these
measures on the performance of the random forest model.

For simplicity, we will deal with the hypothetical situation
in which a single ISI was used for paired stimulations. All
of our results generalize to different inter-stimulus intervals.

Let $k$ be the number of experimental subjects in some
subject group $\mathcal{G}$, to each of whom $n$ paired stimulations and
$m$ test stimulations were elicited.

Let $\textbf{P}^{n \times k}, \textbf{T}^{m\times k}$ be matrices over the
vector space $\mathbb{R}^+$ representing
the paired and test potentials evoked across each of the $k$ subjects.

\end{definition}

\begin{definition} 
    Let $x \in \textbf{P}_{\star i}$ be the MEP of a single paired stimulation
    elicited on the $i$th experimental subject, and $\textbf{t} =
    \textbf{T}_{\star i}$ the vector containing the MEPs of all test pulses
    elicited on that subject. Let $\textbf{w}$ be some appropriate weight
    vector. Then we define two pulse-specific relative amplitude measures,

    \begin{equation} 
        \delta(x) := \frac{x}{m}\sum_{j=1}^m\frac{1}{t_j} 
    \end{equation}

    \begin{equation}
            \rho_w(x) &:= \frac{xm\sum_{j=1}^m w_j}{\sum_{j=1}^m t_j w_j} \\ 
    \end{equation}

    \begin{equation}
        \delta_w(x) &:= \frac{\frac{x}{m}\sum_{j=1}^m\frac{w_j}{t_j}}{\sum_{j=1}^mw_j} 
    \end{equation}
\end{definition}

Notice as well that $\rho$ and $\delta$ are defined over the test pulses in a
specific experimental session $i$. In other words, whenever we speak of the
$\delta$ and $\rho$ \textit{features} (\textit{id est}, of the data resulting from
broadcasting $\rho$ and $\delta$ over a series of observations), such feature is
understood to be subject- and session-specific.

In particular, $\rho$ is a representation of the relative importance of each
double pulse in relation to the overall distribution of the test pulses in the
subject. It measures the deviation of the double pulse $x$ with respect to the
average test pulse. On the other hand, $\delta$ is a measure of the
proportionality of a double pulse with respect to different values in the
distribution of the test pulses of the subject.

\subsection{ML model without relative amplitude measures}

When trained on the raw data, without the inclusion of pulse-specific relative
amplitude measures, the model's accuracy was of $\approx34.2 \%$. However, the
confusion matrix of the model shows the errors are concentrated on the healthy
control categories, while categorization of diagnosed subjects was substantially
better. This implies major depressive subjects show statistically significant
and distinct patterns in their TMS responses in comparison to healthy controls,
and may be considered evidence for depression-induced differences in
neuroplasticity.

\end{multicols}

\centering
~

\includegraphics[scale=0.4]{cm-raw}

\justifying
\begin{multicols}{2}

\subsection{Engineered data}

With the inclusion of the $\rho$ feature, accuracy increases by a factor of
$\approx 2.1$ to $72.6\%$. The inclusion of the $\delta$ feature alone increased
it, in comparison to the raw data, had a more or less equivalent impact,
increasing accuracy to $73.4\%$.

\end{multicols}
\raggedright

@@

\includegraphics[scale=0.24]{cm-rho}
\raggedright
\includegraphics[scale=0.24]{cm-delta}

\justifying
\begin{multicols}{2}

The model still shows a higher accuracy when classifying diagnosed subjects, but
the overall accuracy across all categories was significantly improved.

As stated earlier, the inclusion of the $\delta$ and $\rho$ features computed
over the logarithmically transformed EMG peak-to-peak improved the model's
accuracy. Concretely, accuracy was increased to $86\%$, with the following
confusion matrix.

\end{multicols}

~
\centering

\includegraphics[scale=0.4]{cm-dr-ln}

\justifying
\begin{multicols}{2}

At last, if to the previous model we add also the weighted versions of $\delta$
and $\rho$, using inverse-variance weights, we obtained an accuracy of $89.8\%$,
with the following confusion matrix.

\end{multicols}

\centering
~

\includegraphics[scale=0.4]{final-cm}

\justifying
\begin{multicols}{2}

\section{Statistics}

\begin{wrnote}
    The description of the experimental process in this section is poor. Also I
    do not know the total number of subjects, experiments are still being
    conducted. Need input from the lab on these matters.
\end{wrnote}

Although distributions were always exponential, the $\beta$ parameter of said
distributions varied across subject groups and session types.

@@

Each of the means in the above table correspond to the estimated $\beta$
parameter of the distribution of the paired pulses on each subject group.

\end{multicols}
\raggedright

\includegraphics[scale=0.14]{Paired-TestDist}
\raggedright
\includegraphics[scale=0.14]{P-dist-subjects-big}

\justifying
\begin{multicols}{2}

@@

The previous results show that the inclusion of pulse-specific relative
amplitude measures greatly improve the accuracy of a random forests model
trained over TMS data for subject classification. More importantly, it becomes
clear that, via the engineered features $\delta$ and $\rho$, researchers can
attain evidence in favour or against hypotheses pertaining to differences among
subject groups. Particularly, in showing that pulse-specific measures of
relative amplitude are significant information to determine the sleep session
and group of a subject, and being relative amplitude measures a proxy for
neuroplasticity, the previous model provides evidence in favour of
sleep-modulated, depression-induced differences in neuroplasticity.

The use of machine learning models over neuroscientific observations is not only
a promising tool in the production of evidence. There is a diagnostic potential
that is still to be evaluated. Indeed, if machine learning models can detect the
neural patterns that distinguish, under specific experimental conditions,
healthy control from diagnosed subjects, such models can potentially be
implemented in the diagnosis process as powerful clinical tool.

Although long and serious scientific effort is still required to appraise the
diagnostic potential of machine learning models, we believe our results allow
for a certain amount of conservative optimism on the matter.

In short, pulse-specific relative amplitude features are successful in making
machine learning models applicable to TMS experimental data. Thus, they can play
an important part in future research by allowing for new ways of analyzing and
extracting meaningful information of TMS results.

\section{Appendix 1}

\section{Appendix 2}

>>>>

\documentclass{article}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{float}
\usepackage{ragged2e}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{pmboxdraw}
\usepackage{graphicx} \graphicspath{
{./images/} }
\usepackage{indentfirst}
\usepackage{multicol}
\usepackage[a4paper, total={6.5in, 8.5in}]{geometry}
\DeclareSymbolFont{letters}{OML}{ztmcm}{m}{it}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{wrnote}{Writing note}
\newtheorem{proof}{Proof}

@@

The emergence of new computational models has provided neuroscientists with
novel ways of extracting significant insights from experimental data. This paper
takes a computational approach to challenges arising from the analysis of
transcranial magnetic stimulation (TMS) data under the double pulse paradigm. We
argue that using indicators of neuroplasticity for each specific double
stimulation, as opposed to their average, allows for the use of data-driven
methods of analysis.

Particularly, we formulate pulse-specific measures of relative amplitude between
paired and test pulses. These measures represent the proportionality of specific
paired-pulse responses with respect to test-pulse responses. Namely, they serve as
proxies for neuroplasticity in the brain by capturing the degree of
inhibition or facilitation induced by each double-stimulation.

The benefits of data-driven methods of analysis cannot be overstated. Their
potential implication in the production of scientific evidence and the
diagnosis of clinical disorders go beyond the scope of this paper and deserve
further investigation.

@@

In the context of this paper, we shall term any coefficient that serves to
represent the proportional relationship between the potentials evoked by paired
and test pulses a \textit{measure of relative amplitude} (MRA).

The goal of this paper is to provide pulse-specific measures of relative
amplitude. This is, coefficients that represent the relative amplitude of each
individual paired pulse with respect to the set of test pulses in an
experimental session. The benefit of this is that it keeps data resolution at
its highest, which allows for the implementation of data-driven artificial
intelligence in the analysis of the experimental results. Thus, from a computer
science perspective, our objective is constrained to the sphere of feature
engineering.

@@

\section{Dataset}

Our case study uses data from $N = 43$ subjects at UPenn's \textit{Lab for the
Study of Slow-wave sleep activity}, with $H = 17$ healthy controls (HC) and $D =
26$ with major depressive disorder (MDD). Subjects received transcranial
magnetic stimulation of the motor cortex after both a night of baseline sleep
and a night of slow-wave disruption (SWD) sleep. The stimulations were performed
under the double pulse paradigm. Per session, subjects received twenty-four
($24$) test pulses in total and eight ($8$) paired pulses per ISI. The ISIs were
$4, 5, 8, 10, 15$ and $20$. The evoked potentials were measured by placing an
EMG electrode on the targeted muscle of the thumb. In the slow-wave disruption
session, we sent a constant auditory stimulus with sufficient strength to
interrupt the normal occurrence of slow-wave sleep, yet not strong enough to
wake the subjects.

Please see the table below to see the resulting subject categories:

@@

@@

\begin{tabular}{ |p{2cm}|p{2cm}|p{2cm}|  }
\hline
& Baseline & Slow-wave disruption \\
\hline
Healthy control & HC BL & HC SWD \\
\hline
Major depressive disorder & MDD BL & MDD SWD \\
\hline
\end{tabular}

@@

Each observation comes from an individual transcranial stimulation. The features
of the resulting database are:

\begin{enumerate}
    \item An $EMG$ variable with the peak-to-peak EMG of each elicited pulse.
    \item A $Label$ categorical feature, which represents the group of
        the subject of each observation. 
    \item An $ISI$ feature that represents the inter-stimulus interval of each
        pulse. A value of $-1$ indicated that the given pulse was a test pulse (no
        inter-stimulus interval).
\end{enumerate}

The distribution of the evoked potentials was always exponential. However, the
$\beta$ parameter of the distribution varies across subject groups and session
types, as shown in Figures \ref{fig:figure1} and \ref{fig:figure2}.

@@

Each of the means in the above table corresponds to the estimated $\beta$
parameter of the distribution of the paired pulses on each subject group.

\begin{figure*}
  \begin{minipage}[b]{0.48\linewidth}
    \centering
    \includegraphics[width=\linewidth]{Paired-TestDist}
    \caption{Distribution of paired and test pulses}
    \label{fig:figure1}
  \end{minipage}
  \hspace{0.04\linewidth}
  \begin{minipage}[b]{0.48\linewidth}
    \centering
    \includegraphics[width=\linewidth]{P-dist-subjects-big}
    \caption{Distribution of paired pulses across subject groups}
    \label{fig:figure2}
  \end{minipage}
\end{figure*}

\section{Limitations of the traditional TMS method of analysis}

Measures of relative amplitude in neuroscience are generally computed at the
subject and group level by repeatedly taking averages. This is natural, since
scientific interest generally resides in evaluating differences across subject
groups. However, it also raises problems pertaining to
the downscaling of the data resolution and the reliability of the resulting values.

The procedure to establish the average relative amplitude of a group of subjects
(for example, healthy controls) is simple. Traditionally, it involves taking the
quotient of the average paired-pulse and the average test pulse responses per
every subject. Next, those quotients are averaged out across all subjects in the
subject group. In short, it is an average of averages.

Although this practice is not arbitrary ---since hypotheses generally deal with differences
across subject groups--- it has three major limitations. Firstly, it implies
greatly downscaling the data resolution, making data-driven methods of analysis
unfeasible. Secondly, potentials evoked by test and paired pulses present a very
high variance (Rossini et. al., 20015; Orth, Snijders and Rothwell, 2003;
Wassermann, 2002), which —being that it is a quotient of two means—  raises
questions about the quality of the representation where relatively few pulses
are elicited. Thirdly, our observations suggest potentials evoked by TMS
stimulations follow an exponential distribution, which puts in question whether
arithmetic means are a reliable measure of central tendency.

To make matters worse, when considering the size of the data across multiple
experimental subjects, the shrinkage in data resolution is far from negligible.
And in times when scientific inquiry can greatly benefit from forms of
artificial intelligence that rely on large amounts of data (e.g. machine
learning), it is clearly limiting to count solely with low-resolution measures
to interpret experimental results.

In light of the technical concerns about the traditional approach, this paper
proposes two pulse-specific relative amplitude measures. This allows for
otherwise unfeasible computational analyses of TMS data, such as the use of
machine learning (ML) models for the detection of different pulse-response
patterns among different groups of clinical subjects.

Pulse-specific measures of relative amplitude are coefficients that represent,
for every experimental subject, the proportionality of each individual
paired-pulse response with respect to the set of \textit{all} test-pulse
responses. From a neuroscientific perspective, they are a proxy for
neuroplasticity at the level of each particular stimulation, measuring the
amount facilitation or inhibition in each specific response. From a
computational perspective, these measures prescind from the need of averaging
paired-pulses out, and thus keep data resolution at its highest.

In order to test these measures, we look at whether they improve the performance
of a ML classification model and in what degree.\footnote{We use a
classification model for practical reasons ---namely, because the samples in our
data were conveniently labeled by subject group and sleep session.} Our case
study is a random forest model in Python tasked with classifying every
observation with the appropriate subject label. In other words, its goal is to
infer, based on the properties of each TMS response, the group of the subject
upon which the stimulation was elicited, as well as the type of sleep session
after which it occurred. Our hypothesis is that pulse-specific measures of relative
amplitude will significantly improve a random forest's performance.

Section \textbf{5} provides the mathematical definitions of our measures of
relative amplitude. Section \textbf{6} discusses the impact of each measure on
the performance of the random forest model. Specifically, section \textbf{6.1}
shows the performance of the model when trained over the raw data (i.e. the
features described in section \textbf{3.1}). Section \textbf{6.2} shows the
performance of the model when including pulse-specific measures of relative
amplitude. Section \textbf{6.3} shows the performance of the model when combining the
pulse-specific measures with logarithmic transformations of the raw data and the
use of weighted instead of arithmetic averages.

As for the computation of these measures, we implemented the formulas of section
\textbf{5.2} for every TMS response using the Julia programming language.

For simplicity, we deal with the hypothetical situation in which a single ISI is
used for paired stimulations in a unique TMS session. Our formulations
generalize easily to different inter-stimulus intervals and multiple
experimental sessions.

Firstly, we need to establish some convenient notation. Let $n$ and $m$ be the
number of paired and test pulses elicited to the subject in the session,
respectively. Let $\textbf{x}$, $\textbf{t}$ be vectors over the $\mathbb{R}^+$
vector space whose components are the evoked potentials of paired and pulse
stimulations, respectively.

    Let $x \in \textbf{x}$ be the evoked potential of a single paired
    stimulation. Then we define two pulse-specific relative amplitude measures,

    \begin{equation} 
        \delta(x) := \frac{x}{m}\sum_{j=1}^m\frac{1}{t_j} 
    \end{equation}
\end{definition}

To put it differently, $\rho$ is a representation of the relative importance of
each double pulse in relation to the overall distribution of the test pulses in
the subject. It measures the deviation of the double pulse $x$ with respect to
the average test pulse. $\delta$, in contrast, measures the proportionality of a
double pulse with respect to different values in the distribution of the test
pulses of the subject.

Notice as well that $\rho$ and $\delta$ are defined over the evoked potentials
of a specific experimental session. In other words, whenever we speak of the
$\delta$ and $\rho$ \textit{features} (\textit{id est}, of the data resulting
from broadcasting $\rho$ and $\delta$ over a collection of evoked potentials),
such features are understood to be subject- and session-specific.

\subsection{Random forest without MRA}

When trained on the raw data ---that is, without the inclusion of pulse-specific
MRA--- the model's accuracy was of $\approx34.2 \%$. However, the confusion
matrix of the model, \textbf{Figure 3}, shows the errors are concentrated on the healthy control
categories, while categorization of diagnosed subjects was substantially better.
This implies major depressive subjects show statistically significant and
distinct patterns in their TMS responses in comparison to healthy controls, and
may be considered evidence for depression-induced differences in
neuroplasticity.

\subsection{Random forest with MRA}

We then trained the model first with the aggregation of the $\rho$ feature, then
with the aggregation of the $\delta$ feature, and then with the aggregation of
both.

With the inclusion of the $\rho$ feature increased accuracy by a factor of
$\approx 2.1$ to $72.6\%$. The inclusion of the $\delta$ feature had a similar
impact, increasing accuracy to $73.4\%$.

\begin{figure}[H]
  \centering
  \subfigure[Raw data]{\includegraphics[width=0.48\textwidth]{cm-raw}}
  \hfill
  \subfigure[$\rho$ and $\delta$ features included.]{\includegraphics[width=0.48\textwidth]{cm-rho-delta}}
  \caption{Compared performance: raw data and data with measures of relative
  amplitude.}
  \label{fig:two_images}
\end{figure}

The inclusion of both the $\delta$ and $\rho$ features computed over the
logarithmically transformed EMG peak-to-peak improved the model's accuracy.
Concretely, accuracy was increased to $86\%$, with the following confusion
matrix.

\subsection{Random forest after $\ln$ transforms and weighted averages}

As stated earlier, action potentials evoked by transcranial magnetic
stimulations follow a Gamma distribution that is very close to the exponential.
(see \textbf{Statistics} section). Experimentation has shown that the inclusion
of weighted variants of the features defined above greatly improves the
performance of a random forest model (see \textbf{Empirical results}).

As stated in section \textbf{3}, we experimented with using weighted
versions of our pulse-specific MRA. They consisted in weighting test pulses
with some appropriate weight vector. For example, including $\rho$ and
$\delta$ using inverse-variance weights, we obtained an accuracy of
$90.2\%$, with the following confusion matrix.

\begin{figure*}
    \centering
    \includegraphics[scale=0.4]{final-cm}
    \caption{Confusion matrix: $\rho(x)$, $\delta(x), \rho(\ln x), \delta(\ln
    x)$, $\rho_w(x)$ and $\delta_w$(x).}
    \label{fig:figure5}
\end{figure*}

@@

The results in \textbf{Section 6} demonstrate that pulse-specific MRA greatly
improve the accuracy of a random forest model trained over TMS data for subject
classification. More importantly, it becomes clear that, by using the engineered
features $\delta$ and $\rho$, researchers can attain evidence in favour or
against hypotheses pertaining to differences among subject groups. Particularly,
the model provides otherwise unattainable evidence in favour of sleep-modulated,
depression-induced differences in neuroplasticity.

\section{Conclusion}

This paper shows that pulse-specific relative amplitude measures allow for the
use of making machine learning models over TMS experimental data. Such models
can play an important part in future research by introducing new ways of
both analyzing and extracting meaningful insights from TMS results.

The use of machine learning models in neuroscientific observations is not only a
promising tool in the production of evidence. There is a diagnostic potential
that is yet to be evaluated. By detecting distinct neural patterns between
healthy control and diagnosed subjects,\footnote{At least under specific
experimental conditions.} these models can potentially serve as a useful tool in
the diagnostic process.

Although long and serious scientific effort is still required to appraise the
diagnostic potential of these technologies, we believe our results allow
for cautious optimism on the matter.

It should however be noted that, although machine learning models reveal
distinct response patterns and differences across subjects, they do not disclose
the neurobiology modulating those differences nor what those patterns are.

Lastly, the impact of pulse-specific MRA in data-driven models other than random forests
is yet to be tested. These empirical trials are not trivial because failure or
success of the models is dependent not only on the engineered features, but on
the nature of the experimental data itself.

\section{Appendix}
